Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystal with and without Void Defect

### 2018-11-09 draft/alexpub.tex
edited

Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig. \ref{fig:deformation-pf} and snapshots of atom configuration at the 10 key points in Fig. \ref{fig:Defect}.  Atoms with ordered orientation  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.

The results show that, at elastic stage(stage\uppercase\expandafter{\romannumeral1}), the structure of model have little change but the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of elastic stage (key point 2). A  great number of dislocation emitted inside $\gamma$ phase stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 in Fig. \ref{fig:Defect}b. The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.  $\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$. The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.

\begin{equation}\label{eq:dis1}
	[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
\end{equation}
The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as

@@

where the pre factor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be obtained under different loading conditions, thus  $\Delta H(\tau^*)$ are different. We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.

>>>>

Deformation process of model without void under uniaxial load is shown by stress-strain curve Fig. \ref{fig:deformation-pf} and snapshots of atom configuration at the 10 key points in Fig. \ref{fig:Defect}.  Atoms with ordered configuration  of $\gamma$ phase grains have been removed in Fig.\ref{fig:Defect}a,\ $\alpha_2$ phase and defects inside grains have been left. Similarly, $\gamma$ phase grain have been removed in Fig. \ref{fig:Defect}b, the defects of $\alpha_2$ phase have been left.

The results show that, at stage \uppercase\expandafter{\romannumeral1}, the structure of the model is under typical elastic deformation and the size of simulation box enlarged due to the loading, the deformation of the two phase are compatible. Emission of dislocation and evolution of defects initiated at the end of stage \uppercase\expandafter{\romannumeral1}. A  great number of dislocation emitted inside $\gamma$ phase at stage 2, however, the dislocation inside $\gamma$ phase was emitted after key point 6 shown by Fig. \ref{fig:Defect}b. The deformation of $\alpha_2$ phase is even more earlier than $\gamma$ phase during yield stage, thus local displacement of two phase are incompatible during yield stage.  $\gamma$ phase (TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2[110] and super dislocations with the Burgers vectors $b=[101]$ and $b=1/2[11\overline{2}]$. 
% The other potential deformation mode is mechanical twinning have been reported along $1/6[11\overline{2}]{111}$, have not been observed in the simulation because of room temperature cannot offer enough energy for dislocation nucleation.

\begin{equation}\label{eq:dis1}
	[\ 0\ 1\ \overline{1}\ ] \to 1/2 [\ 1\ 1\ \overline{2}\ ]+1/2[\ \overline{1}\ 1\ 0\ ]
\end{equation}

The mobility of dislocation is affected by structure of crystal, loading condition and temperature, and experiments have shown that the velocity of dislocation motion is sensitive to stress and temperature\cite{Stein1960}. The brittleness of the two phase Ti-Al alloy attributed to the poor mobility of dislocation at room temperature. The velocity of a screw dislocation can be estimated by Escaig's elastic model \cite{Escaig1968}, it can be written as

@@

where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be obtained under different loading conditions, we chose  $$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$$, thus  $\Delta H(\tau^*)$ are different. We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.
